Blocking-resistant communication\\through domain fronting

### 2014-12-21 docs/meek.tex
switch to non-microscopic IEEEtran class, with placeholder for even-larger 11pt version
Comment about Google pullout of Russia.
light edits/comments up through end of Section 4; more pending

\documentclass{sig-alternate}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}

% Turn off ACM copyright block.
\toappear{}

@@

@@

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Domain fronting enables communication that is apparently with an allowed domain,
but actually with a forbidden domain.
The key idea is the use of different domain names at different layers of communication.
One domain is used on the ``outside'' of an HTTPS request---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---in the HTTP Host header, invisible to the
censor under HTTPS encryption.
We identify a number of hard-to-block web services,
like content delivery networks and Google,
that support fronting because they ignore the outside of an HTTPS request
and dispatch it internally according to the Host header.
If a censor is unable to distinguish fronted circumvention traffic and non-fronted ordinary traffic,
then blocking fronted traffic means blocking an entire web service,
with resulting expensive collateral damage.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy
that decodes a sequence of HTTP requests and feeds their contents into Tor.
A censor sees only a sequence of HTTPS requests to an allowed domain.
We describe our experience with deploying \meek.
% \meek, or something based on it,
% has been adopted by other circumvention systems including
% [blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

@@

Censorship is a daily reality for many Internet users.
Workplaces, schools, and governments use technical and social means
to prevent access to information by the network users under their control.
In response, those users use technical and social means
to gain access to the forbidden information.
What has emerged is an ongoing conflict between censor and censored,
with advances on both sides, more subtle evasion being countered by more powerful detection.

What we as circumventors have in our favor is the censor's
distaste for ``collateral damage,''
accidental overblocking committed in the course of trying to censor something else.
One way to win against censorship is to entangle circumvention traffic
with ordinary Internet traffic in a way that both must be blocked together,
or not at all.
If the ordinary traffic is valuable enough,
above the censor's tolerance for overblocking,
then the circumvention traffic will get through.

In this paper we describe ``domain fronting,'' a general-purpose technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind an HTTPS frontend server.
These include such high--collateral damage infrastructure as
big content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
See Section~\ref{sec:survey} for a list of suitable services.
Domain fronting can be used to tunnel traffic
to a general-purpose proxy,
so that circumvention is not limited only to HTTPS, nor to the domains of any specific web service.

The key idea of domain fronting is the use of
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three places relevant to the discussion:
in the DNS query,
in the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
and in the HTTP Host header~\cite[Section~14.23]{rfc2616}.
Usually, the same domain name appears in all three places.
But in a domain-fronted request,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
which is hidden from the censor by HTTPS encryption,
carries another (the actual destination).

@@

The censor may block neither the DNS request nor the SNI without
collaterally blocking the front domain.
The Host header is invisible to the censor,
but visible to the server receiving the HTTPS request,
which uses the header to internally route the request to its destination.
No traffic ever reaches the front domain,
which may be oblivious to the circumvention.
For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
domain fronting can be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

This Wget command shows domain fronting in action
on Google's infrastructure.
Here, an HTTPS request for \urll{www.google.com} has a Host header for
\urll{maps.google.com}. The HTML in the response is that of Google Maps.

@@

A variation on fronting is ``domainless'' fronting,
in which there is no DNS request and no SNI.
It looks to the censor
like the user is browsing an HTTPS site by its IP address,
or using a web client that doesn't support SNI.
Domainless fronting can be useful when there is no known front domain
with sufficiently high collateral damage.
The censor is faced with the choice of blocking an entire IP address, not only a domain;
blocking requests without SNI;
or trying to find some other, presumably more expensive, test to distinguish
circumvention traffic.

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as pluggable transport~\cite{pt} for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received by the server from Tor
are returned to the client within HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

@@

\meek\ has been built into an experimental release of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront
as intermediate web service backends.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:survey} names other fronting-capable services
and Section~\ref{sec:discussion} describes other possible deployments.
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems including
[blinded for anonymous submission].
% ANON
% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

@@

Domain fronting and HTTPS take care of two big circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
Our goal is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than domain blacklists or deep packet inspection---to
force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to traffic analysis
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek\
to samples of HTTPS traffic at a network router.

To our knowledge,
the earliest application of domain fronting to circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Fronting has also been used with success since 2013
for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
GoAgent and flash proxy are the systems that most directly
inspire ours.

@@

Broadly speaking, there are two main challenges in circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents of the communication may be.
A savvy censor will use both means of censorship, and
effective circumvention requires countering both.

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
Then a connection is successful, the server can be blacklisted.
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up on observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

There are two general strategies for countering content-based blocking.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the so-called ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Good examples of look-like-nothing transports are
obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
Both obfs2 and obfs3 work by superenciphering an underlying stream,
using a key exchange that has no plaintext components.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in its
payload obfuscation, but additionally obscures its traffic signature
(packet lengths and timing), and is designed to resist active probing.
A ScrambleSuit server will accept a TCP connection but not send a reply
until the client proves knowledge of a shared secret.
obfs4~\cite{obfs4}
(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.

@@

Houmansadr et~al.~\cite{parrot} evaluate ``parrot'' systems that imitate another protocol
and conclude that unobservability by imitation is fundamentally flawed.
To fully mimic a complex and sometimes proprietary protocol like Skype
is difficult,
because the system must imitate not only the normal operation of the protocol,
but also its reaction to errors,
its typical traffic patterns, and quirks of implementations.
Geddes et~al.~\cite{acks}
demonstrate that even non-parrot systems may be vulnerable to
attacks that disrupt circumvention while having little effect
on ordinary traffic.
Their examination includes VoIP protocols,
in which packet loss and duplication are acceptable.
The censor may, for example, strategically drop certain packets
in order to disrupt a covert channel, without much harming ordinary VoIP calls.

The other grand challenge of proxy-based circumvention is address-based blocking.
Tor has long faced the problem of the blocking of its relays,
the addresses of which appear in a public directory.
In response, Tor began to reserve a portion of its
new relays as secret ``bridges''~\cite{tor-blocking}
whose addresses are not publicly known.
BridgeDB, the database of secret bridges,
carefully distributes bridge addresses
so that anyone can learn a few bridges, but it is hard to learn all of them.
BridgeDB uses captchas and other rate-limiting measures,
and over short time periods,
always returns the same set of bridges to the same requester,
preventing enumeration by simple repeated queries.
BridgeDB is also capable of distributing the addresses
of obfuscated bridges (obfs3 or ScrambleSuit);
the combination
of careful bridge address distribution and obfuscated protocols
gives Tor's system a realistic claim to addressing both main challenges of circumvention.
Address distribution appears to be the weaker side of the defense,
as evidenced by real-world censors' apparent preference for
blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data...},
where ``\textsl{data...}'' is the URL-embedded message the client wants to send.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
an unblockable web service takes the place of the front domain,
and the destination of the communication is embedded somewhere in an HTTPS query
rather than in the Host header.

Decoy routing~\cite{decoyrouting}
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
For this reason, it is also called end-to-middle proxying.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that lie
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing:
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it doesn't require knowing cooperation by network intermediaries.

@@

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path component of a URL.
For example, in the S3 URL
\urll{https://s3.amazonaws.com/bucketname/filename},
the censor only gets to ``see'' the generic domain part, ``\urll{s3.amazonaws.com}''.
The path component ``\urll{/bucketname/filename}'',
which would reveal the use of CloudTransport,
cannot be used for blocking because it is encrypted inside HTTPS.

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
domain fronting with App Engine.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
It also uses App Engine, but uses a socket API rather than a URL fetch API,
in order to support protocols other than HTTP and HTTPS.
Cloud-Entry has the same problem with NAT that flash proxy does,
because the proxy tries to connect back to the client with a socket.
App Engine kills web requests (and their associated socket connections)
when they take longer than 60~seconds,
so users must reconnect at least that often.

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
% ANON
% Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
% ANON
% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

@@

The client,
intermediate web service,
and destination proxy
are uncontrolled by the censor.
The censor does not control a TLS certificate authority;
specifically it cannot man-in-the-middle an HTTPS session
without being caught by ordinary certificate verification.
The client has a way to get a copy of the necessary client programs.

>>>>

% \documentclass{sig-alternate}
\documentclass{IEEEtran}
% \documentclass[11pt]{IEEEtran}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{color}

% Turn off ACM copyright block.
% \toappear{}

@@

\newcommand{\note}[1]{{\textcolor{red}{[\textit{#1}]}}}
\newcommand{\vp}[1]{\note{#1 --VP}}

@@

\begin{abstract}
\vp{This abstract is quite long}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Domain fronting enables communication that is apparently with an allowed domain,
but actually with a forbidden domain.
The key idea is the use of different domain names at different layers of communication.
One domain is used on the ``outside'' of an HTTPS request---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---in the HTTP Host header, invisible to the
censor under HTTPS encryption.
We identify a number of hard-to-block web services,
like content delivery networks and Google,
that support fronting because they ignore the outside of an HTTPS request
and dispatch it internally according to the Host header.
If a censor is unable to distinguish fronted circumvention traffic and non-fronted ordinary traffic,
then blocking fronted traffic means blocking an entire web service,
resulting in expensive collateral damage.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines
\vp{What is the point of the backslash-space after \meek here?  The
backslace-xspace already takes care of the trailing whitespace.}
fronting with an HTTP-based tunneling proxy
that decodes a sequence of HTTP requests and feeds their contents into Tor.
A censor sees only a sequence of HTTPS requests to an allowed domain.
We describe our experience with deploying \meek.
% \meek, or something based on it,
% has been adopted by other circumvention systems including
% [blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

@@

Censorship is a daily reality for many Internet users.
Workplaces, schools, and governments use technical and social means
to prevent access to information by the network users under their control.
In response, those users employ technical and social means
to gain access to the forbidden information.
We have seen
an ongoing conflict emerge between censor and censored,
with advances on both sides, more subtle evasion being countered by more powerful detection.

We as circumventors have in our favor the censor's
distaste for ``collateral damage'':
accidental overblocking committed in the course of trying to censor something else.
One way to win against censorship is to entangle circumvention traffic
with ordinary Internet traffic such that both must be blocked together,
or not at all.
If the ordinary traffic is valuable enough,
above the censor's tolerance for overblocking,
then the circumvention traffic will get through.

In this paper we describe ``domain fronting,'' a general-purpose technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind an HTTPS frontend server.
These include such high-collateral-damage infrastructure as
big content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
(See Section~\ref{sec:survey} for a list of suitable services.)
Domain fronting can be used to tunnel traffic
to a general-purpose proxy,
so that circumvention is not limited only to HTTPS, nor to the domains of any specific web service.

The key idea of domain fronting is the use of
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three places relevant to the discussion:
in the DNS query,
in the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
and in the HTTP Host header~\cite[Section~14.23]{rfc2616}.
Usually, the same domain name appears in all three places.
In a domain-fronted request, however,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
which is hidden from the censor by HTTPS encryption,
carries another (the actual destination).

@@

The censor can block neither the DNS request nor the SNI without
collaterally blocking the front domain.
The Host header is invisible to the censor,
but visible to the server receiving the HTTPS request,
which uses the header to internally route the request to its destination.
No traffic ever reaches the front domain,
which may be oblivious to the circumvention.
For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
domain fronting can be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

This Wget command shows domain fronting in action
on Google's infrastructure.
Here, an HTTPS request for \urll{www.google.com} has a Host header for
\urll{maps.google.com}, even though the SNI in the TLS handshake specifies
\texttt{www.google.com}.
The HTML in the response is that of Google Maps.

@@

A variation on fronting is ``domainless'' fronting,
in which there is no DNS request and no SNI.
It looks to the censor
like the user is browsing an HTTPS site by its IP address,
or using a web client that does not support SNI.
Domainless fronting can be useful when there is no known front domain
with sufficiently high collateral damage.
The censor is faced with the choice of blocking an entire IP address, not only a domain;
blocking requests without SNI;
or trying to find some other, presumably more expensive, test to distinguish
circumvention traffic.

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a pluggable transport~\cite{pt} for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received by the server from Tor
are returned to the client within HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

@@

\meek\ has been built into an experimental release of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront
as intermediate web service backends.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:survey} names other fronting-capable services
and Section~\ref{sec:discussion} describes other possible deployments.
\vp{It's confusing here having out-of-order references to sections.  This
also occurs below}
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems including
[blinded for anonymous submission].
% ANON
% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

@@

Domain fronting and HTTPS address two major circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
Our goal is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than domain blacklists or deep packet inspection---to
force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to traffic analysis
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek\
to samples of HTTPS traffic at a network router.

\vp{Seems this should go in the next section instead}
To our knowledge,
the earliest application of domain fronting to circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Fronting has also been used with success since 2013
for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
GoAgent and flash proxy are the systems that most directly
inspire ours.

@@

Broadly speaking, there are two main challenges in circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, regardless of
the contents of the communication.
A savvy censor will use both means of censorship, and
effective circumvention requires countering both.

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
Then a connection is successful, the server can be blacklisted.
\vp{Try not to begin sentences with ``Then'' (or with conjunctions like
``But'').  Also, the writing has a lot of passive voice here.}
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up on observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

There are two general strategies for countering content-based blocking.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the so-called ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Examples of look-like-nothing transports are
obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
Both obfs2 and obfs3 work by superenciphering
\vp{not clear here what superenciphering means; presumably, it's a reference
to encrypting a stream that's already encrypted, but the reader has to pause
and work that out}
an underlying stream,
using a key exchange that has no plaintext components.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in its
payload obfuscation, but additionally obscures its traffic signature
(packet lengths and timing), and is designed to resist active probing.
A ScrambleSuit server will accept a TCP connection but not send a reply
until the client proves knowledge of a shared secret.
\vp{Say, has there been any work on using port-knocking to resist active
probing?}
obfs4~\cite{obfs4}
(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.

@@

Houmansadr et~al.~\cite{parrot} evaluate ``parrot'' systems that imitate another protocol
and conclude that unobservability by imitation is fundamentally flawed.
To fully mimic a complex and sometimes proprietary protocol like Skype
is difficult,
because the system must imitate not only the normal operation of the protocol,
but also its reaction to errors,
its typical traffic patterns, and quirks of implementations.
Geddes et~al.~\cite{acks}
demonstrate that even non-parrot systems may be vulnerable to
attacks that disrupt circumvention while having little effect
on ordinary traffic.
Their examination includes VoIP protocols,
in which packet loss and duplication are acceptable.
The censor may, for example, strategically drop certain packets
in order to disrupt a covert channel, without much harming ordinary VoIP calls.
\vp{The above could be compressed somewhat to save room}

The other grand challenge of proxy-based circumvention is address-based blocking.
Tor has long faced the problem of the blocking of its relays,
the addresses of which appear in a public directory.
In response, Tor began to reserve a portion of its
new relays as secret ``bridges''~\cite{tor-blocking}
whose addresses are not publicly known.
BridgeDB, the database of secret bridges,
carefully distributes bridge addresses
so that anyone can learn a few bridges, but it is hard to learn all of them.
BridgeDB uses CAPTCHAs and other rate-limiting measures,
and over short time periods,
always returns the same set of bridges to the same requester,
preventing enumeration by simple repeated queries.
BridgeDB is also capable of distributing the addresses
of obfuscated bridges (obfs3 or ScrambleSuit);
the combination
of careful bridge address distribution and obfuscated protocols
gives Tor's system a realistic claim to addressing both main challenges of circumvention.
Address distribution appears to be the weaker side of the defense,
as evidenced by real-world censors' apparent preference for
blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A drawback with flash proxy's use of the browser is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data...},
where ``\textsl{data...}'' is the URL-embedded message the client wants to send.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
an unblockable web service takes the place of the front domain,
and the destination of the communication is embedded somewhere in an HTTPS query
rather than in the Host header.
\vp{Sketch the limitations of this approach}

\vp{Lots of passive in this paragraph}
Decoy routing~\cite{decoyrouting}
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
For this reason, it is also called end-to-middle proxying.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that reside
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing:
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it does not require active cooperation by network intermediaries.

@@

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path component of a URL.
For example, in the S3 URL
\urll{https://s3.amazonaws.com/bucketname/filename},
\vp{should ``filename'' in the URL be italicized?  It sounds like it's
a generic placeholder, not a literal}
the censor only gets to ``see'' the generic domain part, ``\urll{s3.amazonaws.com}''.
The path component ``\urll{/bucketname/filename}'',
which would reveal the use of CloudTransport,
cannot be used for blocking because it is encrypted inside HTTPS.

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
domain fronting with App Engine.
\vp{Was it literally an inspiration, or was it concurrent development?
I thought it was more the latter.}
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent does not use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload
\vp{``generally'' upload---what's their practical alternative?}
their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014,
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
\vp{Add mention of what \meek\ platforms still worked.}
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
It also uses App Engine, but via a socket API rather than a URL fetch API,
in order to support protocols other than HTTP and HTTPS.
Cloud-Entry has the same NAT problem as flash proxy,
because the proxy tries to connect back to the client with a socket.
App Engine kills web requests (and their associated socket connections)
when they take longer than 60~seconds,
so users must reconnect at least that often.

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
% ANON
% Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
% ANON
% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
\vp{Explain Pisphon's relevance to meek}

@@

The client,
intermediate web service,
and destination proxy
are uncontrolled by the censor.
The censor does not control a trusted TLS certificate authority;
specifically it cannot man-in-the-middle an HTTPS session
without being caught by ordinary certificate verification.
The client has a way to get a copy of the necessary client programs.
